Taxonomic level search

### 2023-03-17 workflow/notebooks/tax-search.Rmd
Plot ASVs too

```{r load_data}
results_dat <- data.table::fread(here('results', 
                                      'performance_results_aggregated.csv')
                                 ) %>% 
  rename(train = cv_metric_AUC,
         test = AUC,
         AUPRC = prAUC) %>% 
  pivot_longer(c(train, test), names_to = 'set', values_to = 'AUROC') %>% 
  mutate(taxlevel = factor(taxlevel, levels = c("order", "family", "genus", "OTU")))
```

@@

```{r tax-search_perf}
results_dat %>% 
  ggplot(aes(x = taxlevel, y = AUROC, color = set)) +
  geom_hline(yintercept = 0.5, linetype = 'dashed') +
  geom_boxplot() +
  facet_wrap(~outcome, nrow = 1) +
  theme_sovacool()
```

>>>>

```{r load_data}
results_dat <- data.table::fread(here('results', 
                                      'performance_results_aggregated.csv')
                                 ) %>% 
  rename(train = cv_metric_AUC,
         test = AUC,
         AUPRC = prAUC) %>% 
  pivot_longer(c(train, test), names_to = 'set', values_to = 'AUROC') %>% 
  mutate(taxlevel = factor(taxlevel, levels = c("order", "family", "genus", "OTU", 'asv')))
```

@@

```{r tax-search_perf}
results_dat %>% 
  ggplot(aes(x = taxlevel, y = AUROC, color = set)) +
  geom_hline(yintercept = 0.5, linetype = 'dashed') +
  geom_boxplot() +
  facet_wrap(dataset~outcome)+#, nrow = 1) +
  theme_sovacool()
```
